Preliminary Experiment

### 2018-01-18 preliminary/preliminary_report.tex

Considered Bandit Prior/Instances that were considered (only for 10 arms). :
\begin{enumerate}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``Heavy-tailed": For ease we simply took the 10 arms to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$)
\item Needle-in-haystack
\begin{enumerate}
\item Low Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.01, 1 arm with mean 0.02 (+ 0.01)
\item Medium - 9 arms with mean 0.01, 1 arm with mean 0.06 (+ 0.05)
\item High - 9 arms with mean 0.01, 1 arm with mean 0.21 (+ 0.20)
\end{enumerate}
\item Medium Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.50, 1 arm with mean 0.01 (+ 0.01)
\item Medium - 9 arms with mean 0.50, 1 arm with mean 0.55 (+ 0.05)
\item High - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\item High Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.80, 1 arm with mean 0.81 (+ 0.01)
\item Medium - 9 arms with mean 0.80, 1 arm with mean 0.85 (+ 0.05)
\item High - 9 arms with mean 0.80, 1 arm with mean 1.0 (+ 0.20)
\end{enumerate}
\end{enumerate}
\end{enumerate}

@@

The first run considered $N=50$ runs which didn't seem to be able to differentiate between the learning rates of the particular algorithms. However, it was helpful for reducing the space of needle in haystack algorithms. Originally we considered three regimes of ``needle-in-haystack" instances since we weren't sure if learning would be different between the different regimes. We considered so many needle-in-haystack instances to see if there would be meaningful qualitative differences between learning when the means were at extremes vs when most means were in the middle of the range of possible means. \\

The plots for all the algorithms are reported below. The ``low" $\Delta$ in the needle-in-haystack appears uninteresting across all considered means, likely becuase the $\Delta$ of $0.01$ is too small to be meaningful. For the ``medium" instances it appears as though there is a qualitative difference between the ``low" mean and the others. Though this may be partially due to low $N$, it appears as though there is some divergence particularly between UCB and Thompson Sampling. For the high $\Delta$ it the ``low" mean and ``medium" mean seem to have qualitatively similar results. The ``high" mean has starker differences in terms of the learning rates of the algorithms.

@@

The plots with all the algorithms are reported below:
The high range: \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - Medium 3"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - High 1"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Heavy Tail 3"}
\\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Uniform 3"}
\\

@@

The rate of learning for UCB seems slower than for the other algorithms. Is this expected (or do we need to tune the UCB1 constant)? It appears that UCB does not catch up to Dynamic $\epsilon$-greedy until $t = 1500$. This potentially explains the results we saw that UCB1 loses in the competing bandits game because it's rate of learning growth for these bandit instances is slower than the other algorithms.

@@

>>>>

Bandit Prior/Instances that were considered (only for 10 arms):
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item Low Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.01, 1 arm with mean 0.02 (+ 0.01)
\item Medium - 9 arms with mean 0.01, 1 arm with mean 0.06 (+ 0.05)
\item High - 9 arms with mean 0.01, 1 arm with mean 0.21 (+ 0.20)
\end{enumerate}
\item Medium Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.50, 1 arm with mean 0.01 (+ 0.01)
\item Medium - 9 arms with mean 0.50, 1 arm with mean 0.55 (+ 0.05)
\item High - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\item High Mean
\begin{enumerate}
\item Low - 9 arms with mean 0.80, 1 arm with mean 0.81 (+ 0.01)
\item Medium - 9 arms with mean 0.80, 1 arm with mean 0.85 (+ 0.05)
\item High - 9 arms with mean 0.80, 1 arm with mean 1.0 (+ 0.20)
\end{enumerate}
\end{enumerate}
\end{itemize}

@@

The first run considered $N=50$ runs. The main use of this run was to help us detect any qualitative differences between the different needle-in-haystack regimes we  Originally we considered three regimes of ``needle-in-haystack" instances since we weren't sure if learning would be different between the different regimes. We considered so many needle-in-haystack instances to see if there would be meaningful qualitative differences between learning when the means were at extremes vs when most means were in the middle of the range of possible means. \\

The plots for all the algorithms are reported below. The ``low" $\Delta$ in the needle-in-haystack appears uninteresting across all considered means, likely because the $\Delta$ of $0.01$ is too small to be meaningful. For the ``medium" instances it appears as though there is a qualitative difference between the ``low" mean and the others. Though this may be partially due to low $N$, it appears as though there is some divergence particularly between UCB and Thompson Sampling. For the high $\Delta$ it the ``low" mean and ``medium" mean seem to have qualitatively similar results. The ``high" mean has starker differences in terms of the learning rates of the algorithms. \\

@@

The plots with all the algorithms are reported below: \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - Medium 3"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - High 3"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Heavy Tail 3"}
\\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Uniform 3"}
\\

@@

The rate of learning for UCB seems slower than for the other algorithms. Is this expected (or do we need to tune the UCB1 constant - I don't think so)? This potentially explains the results we saw that UCB1 loses in the competing bandits game because it's rate of learning growth for these bandit instances is slower than the other algorithms.

@@

As well, a version of the plots that smooths the trajectory: \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - Medium 3_smooth"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Needle50 - High 3_smooth"} \\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Heavy Tail 3_smooth"}
\\
\includegraphics[scale=0.5]{"../results/Reward Trajectory for Uniform 3_smooth"}
\\
